Spatial Reasoning and Statistical Graphics

### 2014-10-06 Paper/Draft1/TestingVisualAptitude.Rnw
Set ID to be the answer id, then conduct t-tests comparing results from Hillary to those from Stephanie

>>>>

\section*{Appendix}
T-tests of results for Hillary and Stephanie: 
<<ttest, echo=T, include=T>>=
t.test(ans.summary$card_rot[1:18], ans.summary$card_rot[-c(1:18)])
t.test(ans.summary$folding[1:18], ans.summary$folding[-c(1:18)])
t.test(ans.summary$lineup[1:18], ans.summary$lineup[-c(1:18)])
t.test(ans.summary$vis_search[1:18], ans.summary$vis_search[-c(1:18)])
@
